\documentclass[12pt]{report}
\usepackage[a4paper, margin=2.5cm]{geometry}
\pagenumbering{gobble}
\usepackage{hyperref}
\usepackage{tcolorbox}
\newcommand{\student}[3]{\begin{tcolorbox}\noindent Introduction to
    Psycholinguistics (WS2021-2022) \\ Report of \textbf{Paper~#3} by
    \textbf{#1 (#2)} 
  \end{tcolorbox}}



\begin{document}

%% Change:
\student{Shawon Ashraf}{3460184}{3}


\paragraph{APA reference:} 
%report the full reference of the paper in APA style (\href{https://www.library.kent.edu/files/APACheatSheet.pdf}{\underline{Online Guide}})
Trueswell, J. C. (1996). The role of lexical frequency in syntactic ambiguity resolution. \textit{Journal of memory and language}, 35(4), 566-585.

\paragraph{Research Question(s):}
%What are the questions the authors of the paper are addressing?

\begin{enumerate}
    \item Does the frequency of a verb being used as a participle form influence a reader to consider the alternative of a relative clause?
    
    \item Do readers disambiguate syntactic and lexical ambiguities in the same fashion? Or, continuing from the last question, does lexical frequency affect syntactic ambiguity resolution?
    
    \item How much effect does relative frequency of a relative clause has over to its overall frequency when compared to main clauses?
\end{enumerate}

\vfill
\paragraph{Methodology:} 
%which methods are used?

The author divided their experiment in two parts. \textbf{In the first part}, they used moving-window self-paced reading to check how lexical frequency can affect syntactic ambiguity resolution. Two different groups of verbs were used in a self paced read one word at a time task. Half of the verbs had high participle frequency and were called High-PP Verbs while the other half were called Low-PP Verbs for having the opposite amount of participle frequency. All the verbs used in the experiment were morphologically ambiguous. The verbs were paired with nouns to set up an Agent - Patient theme. 

There were fourteen subjects in the experiment, all from University of Pennsylvania. The duration of the first experiment was set to 30 minutes. The subjects in the experiment were also asked to complete sentences based on these verbs to test if a verb's participle frequency can affect the choice of a clause during sentence generation. Half of the subjects attended this study. 

\textbf{The second experiment}  was conducted with the same materials from the first experiment. However, this time in noun-verb pairing they only used nouns which were good agents. The subjects were then asked to rate the sentences based on how good the agent-patient assignment was in a sentence. 

Eighteen subjects from University of Pennsylvania attended the experiment as subjects.
\vfill

\paragraph{Results:} 
%what are the main results?
The results from the first experiment indicated that when the participle frequency of a verb is higher, the readers had very little or no difficulty to comprehend the sentences being used. On the other hand the opposite happened for verbs with low participle frequency with reduced relatives. The results provide answers to the research questions the author had initially  set out for. 

As for the second experiment, the results show that for low participle frequency, the subjects had more difficulty, measured in terms of mean reading times to comprehend a clause and disambiguate it.
\vfill

\paragraph{Personal Opinion:} 
%What did I like, dislike about this
%paper? 
My personal opinions of the the paper are that the research questions were very interesting because the more recent paper tend to show that frequency can affect bias in terms of judgement in automated models. The author have shown in their experiment that this can indeed be the case for human readers as well. However, I would rather pick on the structure of the paper that authors could have combined the results and discussion from both experiments together since one of them is just a slightly modified version of the other. Also, the related work section should have been separated from the main work, as the current structure reads more noisy. I am more used to reading recent technical papers which follow a more separated structure, perhaps my complaints stem from that bias (this paper is from 1996).
\vfill


\end{document}

